Supplementary methods

### 2020-08-30 text/supplemental_methods.Rmd
Combine ktis and kcl into single plot with alpha set to 0.5

```{r sm3, fig.height=3}
pritis = ggplot(data.frame(x=0:30),aes(x)) + stat_function(fun=function(x) dgamma(x,1.2,.2),geom="area",fill="#666699")+
  labs(title=expression(paste("Prior for k"["tis"])),x=expression(paste("k"["tis"])), y = "Probability Density") +
  theme_classic() + scale_x_continuous(limits = c(0, 20), breaks = c(seq(0,20, by =5))) +
  scale_y_continuous(limits = c(0,0.75), breaks = c(seq(0,0.75, by = 0.25))) + theme(title = element_text(size = 10))

pricl = ggplot(data.frame(x=0:30),aes(x)) + stat_function(fun=function(x) dgamma(x,3.5,2.5),geom="area",fill="#666699")+
  labs(title=expression(paste("Prior for k"["class"])),x=expression(paste("k"["cl"])), y = "Probability Density") +
  theme_classic() + scale_x_continuous(limits = c(0, 20), breaks = c(seq(0,20, by =5))) +
  scale_y_continuous(limits = c(0,0.75), breaks = c(seq(0,0.75, by = 0.25))) + theme(title = element_text(size = 10))
print(pritis+pricl)
```

>>>>

```{r sm3, fig.height=3, fig.width=3}
ggplot(data.frame(x=0:30),aes(x)) + 
  stat_function(fun=function(x) dgamma(x,1.2,.2),geom="area", aes(fill = "ktis"))+ 
  stat_function(fun=function(x) dgamma(x,3.5,2.5),geom="area", aes(fill = "kcl"))+ 
  labs(title=expression(paste("Prior for k"["tis"], "and k"["cl"])),x= "k value", y = "Probability Density") +
  theme_classic() + scale_x_continuous(limits = c(0, 20), breaks = c(seq(0,20, by =5))) +
  scale_y_continuous(limits = c(0,0.75), breaks = c(seq(0,0.75, by = 0.25))) +
  scale_fill_manual(values = c(alpha("#E69F00", 0.5),alpha("#0072B2", 0.5)),
                    labels = c(expression(paste("k"["cl"])), expression(paste("k"["tis"])))) +
  theme(plot.title = element_text(size = 12, hjust = 0.5),
        panel.grid.major = element_line(size = 0.75),
        panel.grid.minor = element_line(),
        legend.position = c(0.8, 0.8),
        legend.spacing.y = unit(0, "mm"),
        legend.title = element_blank(),
        legend.text = element_text(size = 8),
        legend.key.size = unit(0.75,"line"),
        legend.background = element_blank(),
        legend.box.background = element_rect(colour = "black"))
```
